Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-08 lqg-strings.tex
added a paragraph about the WS Hamiltonian and momentum operators and rigid rotations of the string

@@

Next we look at the $n$-th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have independent left and right sectors, thus permitting spin-1 states. We'll discuss these closed string single excitation states in section \ref{sec:discussion}. The mass-shell now reads

@@

The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a glaring disadvantage: they do not have WS diffeomorphism invariance, making it so it is not clear what WS parameterization should be used and neither if physical predictions can be extracted from them since it is not obvious that different parameterizations describe the same system. If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS diffeomorphism invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
\begin{multline} \label{eqn:emergent-dimensions-action}
	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
\end{multline}
where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ... \gg m_{d}$. This is Afshordi's model \cite{Afshordi-emergent}. Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
\end{equation}
so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
\begin{equation} \label{eqn:X-masses-constraint}
	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
\end{equation}
where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.

>>>>

A quick calculation reveals that the WS Hamiltonian and momentum operators are given by
\begin{align}
	\Hat{H} & = - \frac{1}{2} \sum _{n} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-Hamiltonian}              \\
	\Hat{P} & = - \frac{1}{2} \sum _{n} \frac{n}{E_{n}} \Hat{\widetilde{L}}_{n , n} \label{eqn:WS-momentum}
\end{align}
since those generate $\tau$ and $\sigma$ translations respectively
\begin{align}
	\left[ \Hat{H} , \Hat{X}^{\mu} \right] & = - i \del _{\tau} \Hat{X}^{\mu} \label{eqn:tau-generator}     \\
	\left[ \Hat{P} , \Hat{X}^{\mu} \right] & = i \del _{\sigma} \Hat{X}^{\mu} . \label{eqn:sigma-generator}
\end{align}
Clearly, $\Hat{P}$ does not necessarily annihilate physical states (see \eqref{eqn:WS-momentum}), thus those are not required to be invariant under rigid rotations of the string. \emph{Physical states for the KG string have non-conserved WS momentum.} Also, we see that there is no level-matching between left and right-moving modes since those are not distinct in our model.

@@

Next we look at the $n$-th excited vector state $\zeta _{\mu} (\Hat{a}^{\mu} _{n})^{\dagger}$ with $\zeta _{\mu} = \zeta _{\mu} (p)$ being the polarization covector. The reason we consider closed string vector states unlike normal String Theory is that in our model, the closed string solution doesn't have distinct left and right sectors, thus permitting spin-1 states. We'll discuss these closed string single excitation states in section \ref{sec:discussion}. The mass-shell now reads

@@

The actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} used in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov} have a clear disadvantage: they lost WS Weyl symmetry, which makes the equations extracted from them have a dependence on the scale factor $\phi (x)$. If we want to formulate an effective stringy action that takes LQG quantum geometric effects into consideration and retains WS Weyl invariance while giving similar results to the analysis done in section \ref{sec:inverse-metric-Polyakov}, we arrive at a similar model as \cite{Afshordi-emergent}, with the action being
\begin{multline} \label{eqn:emergent-dimensions-action}
	S_{ED} = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \sqrt{- g} \big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} \eta _{\mu \nu} + \\
	+ \mu _{0} ^2 \e ^{- m_{\mu} / T} X^{\mu} X^{\nu} \eta _{\mu \nu} \big)
\end{multline}
where $T$ is the \emph{temperature} of target space and the parameters $m_{\mu}$ satisfy an ordering relation $m_{0} \gg m_{1} \gg ... \gg m_{d}$. This is Afshordi's model \cite{Afshordi-emergent}. Where our approach diverges is that we realize the parameters $m_{\mu}$ are constrained by the modified dispersion relations of each field $X^{\mu}$, since as \cite{Bodendorfer-LQG} points out, LQG quantum geometry breaks Lorentz invariance near the Planck scale through modifying the dispersion relation by constraining the free parameters of the model as
\begin{equation} \label{eqn:LQG-modified-dispersion-relation}
	E^2 = m^2 + p^2 + \sum _{n \geq 3} c_{n} \frac{p^n}{E_{pl} ^{n - 2}} ,
\end{equation}
so we note that the mass parameters of the fields $X^{\mu}$ will be constrained as
\begin{equation} \label{eqn:X-masses-constraint}
	E_{\alpha} ^2 = p_{\alpha} ^2 + \sum _{n = 3} ^{D - 1} \frac{m_{n}}{T} \frac{p_{\alpha} ^{n}}{E_{pl} ^{n - 2}} ,
\end{equation}
where $E_{\alpha} ^2$ does not mean $E_{\alpha} E^{\alpha}$, rather it means $(E_{3})^2 , (E_{4})^2 , ... , (E_{D - 1})^2$, \ie, the squared WS energy (and momentum) of each field $X^{\mu}$.
